Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-02-07 paper/main.tex
Add subsection on data smoothing and registration

\section*{Methods}
Our experimental apparatus consisted of a wing and actuator mounted to a
vertical force sensor, with a high-speed color video camera recording the motion
of the wing from a top-down view, and also from a side view using a mirror. The
top-down and side views were used to detect and track the position and
orientation of the wing.  Figure~\ref{fig:apparatus} provides a diagram of the
apparatus as well as illustrations of the three primary variables describing the
wing orientation: Stroke ($\phi$), deflection ($\psi$) and deviation ($\theta$).
The stroke motion is enabled by a hinge joint and is the only actuated degree of
freedom in the system. The deflection of the wing is enabled by a hinge in the
root of the wing, and is a passive motion resulting from both inertial and
aerodynamic effects. Deviation refers to the passive vertical motion of the wing
out of its horizontal flapping plane, and is enabled only by the tolerances of
the hinges and the flexibility of the wing structure itself. These three
variables, and their derivatives, are some of the inputs required to model lift
forces. The other inputs are the geometric and inertial properties of the wings,
obtained from CAD designs and physical measurement. Next, we describe the wing
design and fabrication, the force measurement apparatus, and the method of
extracting wing kinematics from high-speed video.

@@

>>>>

\section*{Methods}
Our experimental apparatus consisted of a wing and actuator mounted to a
vertical force sensor, with a high-speed color video camera recording the motion
of the wing from a top-down view, and also from a side view using a mirror. The
top-down and side views were used to detect and track the position and
orientation of the wing.  Figure~\ref{fig:apparatus} provides a diagram of the
apparatus as well as illustrations of the three primary variables describing the
wing orientation: Stroke ($\phi$), deflection ($\psi$) and deviation ($\theta$).
The stroke motion is enabled by a hinge joint and is the only actuated degree of
freedom in the system. The deflection of the wing is enabled by a hinge in the
root of the wing, and is a passive motion resulting from both inertial and
aerodynamic effects. Deviation refers to the passive vertical motion of the wing
out of its horizontal flapping plane, and is enabled only by the tolerances of
the hinges and the flexibility of the wing structure itself. These three
variables, and their derivatives, are some of the inputs required to model lift
forces. The other inputs are the geometric and inertial properties of the wings,
obtained from CAD designs and physical measurement. Next, we describe the wing
design and fabrication, the force measurement apparatus, and the methods of
extracting and processing wing kinematics data from high-speed video.

@@

\subsection*{Data Smoothing and Registration}
Stroke, deflection and deviation measurements were smoothed with a
Savitzky–Golay filter, providing not only a reduction in noise in the signals
themselves, but also smooth first and second derivatives of these signals. These
kinematic variables were temporally aligned and resampled to the 1 kHz frequency
of the force measurement. Finally, for each wing at each flapping frequency and
amplitude, the data for 10-20 wing strokes were registered and averaged together
to create a composite sample representing the force and kinematics of a single
complete wing stroke of the given wing, frequency and amplitude. These composite
samples were then used for data-driven modeling and analysis.
